---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# swissexchangedata

<!-- badges: start -->
[![R-CMD-check](https://github.com/akhapwoyaco/swissexchangedata/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/akhapwoyaco/swissexchangedata/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/akhapwoyaco/swissexchangedata/branch/main/graph/badge.svg)](https://app.codecov.io/gh/akhapwoyaco/swissexchangedata?branch=main)
<!-- badges: end -->

## Overview

The `swissexchangedata` package, built up for **educational purpose** to learn and sharpen skills in web-scrapping of data from online sources, data wrangling and package development processes.

swisswxchangedata facilitates ease of access of the `Swiss Stock Exchange Market Data News` Via [The SIX Group Newsboard Website](https://www.six-group.com/en/products-services/the-swiss-stock-exchange/market-data/news-tools/newsboard.html#/) via the function: `newsboard_data`.

## Installation

You can install the development version of `swissexchangedata` like so:

``` r
install.packages("devtools") # if you have not installed "devtools" package
devtools::install_github("akhapwoyaco/swissexchangedata")
```

## Usage

This is a basic example which shows you how to solve a common problem:

```{r example}
library(swissexchangedata)
## basic example code
```

Get the data for 9th October 2023 up-to-date:\

```{r}
data_10thOct_2024 <- newsboard_data(firstDate = '2023-10-10', lastDate = Sys.Date())
```


```{r}
head(data_10thOct_2024)
```



## Getting help

If you encounter a clear bug, please file an issue with a minimal reproducible example on GitHub. 

## Code of conduct

Please note that this project is released with a Contributor Code of Conduct. By participating in this project you agree to abide by its terms.

