---
title: "newsboard_data"
output: rmarkdown::html_vignette
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{newsboard_data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{swissexchangedata, rvest}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Introduction to swissechangedata's  newsboard_data() function

This vignette offers a glimpse on the inner functions of the `swissexchangedata`package, built up for **educational purpose** to learn and sharpen skills in web-scrapping of data from online sources, data wrangling and package development.

When extracting the Swiss Stock Exchange data from the [Six Group newsboard](https://www.six-group.com/en/products-services/the-swiss-stock-exchange/market-data/news-tools/newsboard.html#/) website, you must: 

+ Define the `Date Range`, `Message Type`, `Market` and `Products`. 
+ Open in separate view for printing and saving into a pdf file\

The `swissexchangedata` facilitates ease of defining the desired parameters and accessing the data directly into your `workspace`, making use of the currently existing function  news `newsboard_data()`. 

More functions will be added to capture access of data from other tabs provided on the company website. 

The data range capture only 2 years of data, so the stored data requires updating over time to capture most of the data. Looking forward to have various versions of data that update over time.


The scrapped data is cleaned further to add nested data. 

# Data Access

```{r setup}
library(swissexchangedata)
library(rvest)
```


Get the data for September 2023 up-to-date:\

```{r}
all_items_data_sep_2024 <- newsboard_data(firstDate = '2023-10-01', lastDate = Sys.Date())
```

```{r, eval=FALSE}
all_items_data_sep_2024
```

## Data Cleaning

Apparently, the `newsText` column contains further tables on the trades, for which access require further cleaning. The cleaning code is also used in cleaning data package data `swissexchangedata::newsboardmarketdata` and replicated herein.

```{r}
# obtain the preceding text
itemlist_newsText_clean <-function(vec){
  # obtain the preceding text
  read_html(vec) |> html_text()
}
# obtain the data table
itemlist_newsText_table_clean <-function(vec){
  
  # obtain the html tabke from the vector
  temp_obj = read_html(vec) |> html_table(fill=TRUE) #|> unlist()
  # |>  do.call(rbind, lapply(., as.data.frame))
  
  # if no data, skip, else convert to dataframe
  if (!is.null(temp_obj)){
    temp_obj = temp_obj |> as.matrix() |>
      t() |>
      as.data.frame() #|> unlist()
  } else {
    NA
  }
  temp_obj
}
```


```{r}
# get copy of data to all_items_data_sep_2024
all_items_data_sep_2024_original <- all_items_data_sep_2024
# extract text and table from newsText through apply
newsText_column_index <- grep("newsText", colnames(all_items_data_sep_2024))
#
all_items_data_sep_2024$data <- apply(
  X = all_items_data_sep_2024[,newsText_column_index,drop=FALSE],
  MARGIN = 1, simplify = T,
  FUN = itemlist_newsText_clean)
#
all_items_data_sep_2024$table_data <- apply(
  X = all_items_data_sep_2024[,newsText_column_index,drop=FALSE],
  MARGIN = 1, simplify = F,
  FUN = itemlist_newsText_table_clean)
```

## Output

```{r}
all_items_data_sep_2024[1:2,1:15]
```

The data column on trades has been extracted from the HTML paragraph.

```{r}
all_items_data_sep_2024[1,16][[1]][[1]]
```



